A First Look at Celestial Holography

### 2021-04-04 alpha/CelestialHolography/celestial.tex
Add various format tweaks
Add comments on Bondi mass; add some bib

	\begin{figure}[!h]
	\centering
	\includegraphics[width=.5\linewidth]{img/hyperbolicslicing.pdf}
	\caption[Hyperbolic slicing of Minkowski]{
		Hyperbolic slicing of Minkowski, taken from \cite{Strominger:2017zoo}.

@@

@@

\appendix
\section{Symmetries of asymptotically flat spacetime}
	\begin{center}
	\includegraphics[width=.8\linewidth]{img/ASGflat.pdf}
	\end{center}

>>>>

	\begin{figure}[!h]
	\centering
	\includegraphics[width=.45\linewidth]{img/hyperbolicslicing.pdf}
	\caption[Hyperbolic slicing of Minkowski]{
		Hyperbolic slicing of Minkowski, taken from \cite{Strominger:2017zoo}.

@@

	The calculation of conserved charges in gravity is similar to that in gauge theory, but now we already have the symmetry in terms of diffeomorphic generators, thus we need only run the usual Noether's procedure (``forwards'' instead of ``backwards'', compared with what we did in gauge theory), to get the conserved charges.

	Again we integrate the conserved current on the codim-1 $\mcal{I}^\pm$, and it gets reduced to an integral of the codim-2 $CS$ near $i^0$. $\epsilon = 0$ corresponds to $\zeta \propto \pdd{u}$, and the conserved charge is the \textbf{total Bondi mass}; for Kerr spacetimes in the usual conventions, the conserved charge is exactly the mass parameter $M$.

@@

\appendix
\section{Symmetries of asymptotically flat spacetime}
	\vspace{-.5\baselineskip}
	\begin{center}
	\includegraphics[width=.635\linewidth]{img/ASGflat.pdf}
	\end{center}
